
\section{Introduction}
\label{sec:Introduction}

It is expected that a significant fraction of the production cross-section of J/$\psi$ and $\Upsilon$ states in hadron collisions is due to feed-down from heavier 
quarkonium states. A study of this effect is important for the interpretation of onia production cross section and polarization measurements in hadron collisions.  
For P-wave quarkonia, measurements of \chic have been reported by \cdf~\cite{pub:cdf_chic}, HERA-B~\cite{pub:herab_chic} and \lhcb~\cite{pub:lhcb_chic}, 
whereas \cdf~\cite{pub:cdf_chib} and \atlas~\cite{pub:atlas_chib} have performed measurements involving $\chi_b$ states. 
\lhcb has reported`\cite{pub:lhcb_chib} a preliminary measurement of the $\chi_b$ production cross-section, and subsequent decay into \OneS $\gamma$, 
relative to the \OneS production. This measurement was performed on 2011 data, in a region defined by $6 \gevc < \pt(\OneS) < 15 \gevc$ and 
$2.0 < y < 4.5$.  

This note presents an update of the previous \lhcb\ study. Data collected in 2012 were also analyzed, allowing for cross-section measurements at 
\sqs=8\tev. Using the full integrated luminosity allows for a measurement of the differential cross-section in \pt and rapidity bins of the \OneS, and to study the 
production of $\chi_b(2P)$ And $\chi_b(3P)$. A measurement of the $\chi_b(3P)$ mass is also performed by combining data collected in 2011 and 2012. 

The analysis proceeds through the reconstruction of $\Upsilon(nS)$ candidates via their dimuon decays, and their subsequent pairing with a photon to  
look for $\chi_b(mP) \to \Upsilon(nS) \gamma$ decays. Ratios of $\chi_b(mP)$ to $\Upsilon(nS)$ production cross section can be written as

\begin{equation}
    \frac{\sigma(pp \to \chi_b(mP)  \to \Upsilon(nS) \gamma)}{\sigma(pp \to \Upsilon(nS))} = 
    \frac{N_{\chi_b(mP)\to \Upsilon(nS) \gamma}}{N_{\Upsilon(nS)}} \times \frac{\epsilon_{\Upsilon(nS)}}{\epsilon_{\chi_b(mP)\to \Upsilon(nS) \gamma}} = 
    \frac{N_{\chi_b(mP)\to \Upsilon(nS) \gamma}}{N_{\Upsilon(nS)}} \times \frac{1}{\epsilon^{reco}_{\gamma}}
\end{equation}

\noindent where ${N_{\Upsilon(nS)}}$ and ${N_{\chi_b(mP)\to \Upsilon(nS) \gamma}}$ are the $\Upsilon(nS)$ and $\chi_b(mP)$ yields,  
$\epsilon_{\Upsilon(nS)}$ and $\epsilon_{\chi_b(mP)\to \Upsilon(nS) \gamma}$ are their corresponding selection efficiencies. 
The latter are the product of geometric acceptance, trigger efficiency and reconstruction efficiency. Since the selection criteria for the two samples differ only 
in the reconstruction of a photon, the efficiency ratio can be replaced by 1/$\epsilon_{\gamma}$, the reconstruction efficiency for the photon from the $\chi_b$ 
decay. Similar expressions may be used to compute differential cross sections in $\Upsilon$ \pt and rapidity bins. 